Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-04-23 WRITEUP/ms.tex
updated fig

% ------------------
\section{Numerical simulations}\label{sec:sim}
The simulations used in this work are described by \citealt{Pallottini17a, Pallottini17b} and are only briefly summarized here.
%
\ncode{Serra}\footnote{Greenhouse in Italian.} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) techniques to achieve high spatial resolution in regions of interest (e.g., regions of high density).
%
In particular, it uses a modified version of \ncode{ramses}
\citep{Teyssier02a} as the AMR backend. The simulation used here
covers a comoving box of 20\,Mpc $h$\pmOne in size. The simulation
zooms in on a target halo of mass $M_{\rm DM}\simeq10^{11} \Msun$. The Lagrangian
region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter
%mm (equivalent baryonic) 
mass resolution of $\simeq 6\times 10^4 \Msun$, 
%mm ($1.2 \times 10^4 \Msun$) [expanded out the meaning, but check if
%I have it right]  Such
     equivalent at initial density to a baryonic mass resolution of $1.2
     \times 10^4 \Msun$.  This 
region is spatially refined with a quasi-Lagrangian criterion based on
a mass threshold, so that a cell is refined if its total dark matter
plus baryonic mass exceeds the mass resolution by a factor of
eight. The final finest refined cell in the zoom in region has size
$l_{\rm cell}\simeq$\,30\,pc (at $z = 6$). 
%mm
%    \MM{Is this really the resolution of dark matter particles?  The baryonic mass (i.e.\ gas) resolution depends on the 
%    local density, which would have to be specified here.} \AP{the setting description has been extended}
     Cell sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
%mm 
%     \MM{Nota Bene!} \AP{This note is discussed in details in the following section. In the simulation we do not treat 5--10 cells as MCs, so I would remove the point from the present} although the resolved scale of 5--10 cells is rather larger.
The models include a chemical network 
following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and
H$_2^+$ \citep{Grassi14a,Bovino16a}. Of particular importance here is
that abundances are calculated using an on-the-fly non-equilibrium
formation of molecular hydrogen scheme  
%mm following \citet{Pallotini17b} [the order had to be reversed for alphabetization]
    described by \citet{Pallottini17a}.

@@

The local sound speed of all identified molecular complexes is much
smaller than their turbulent velocities\footnote{Velocity dispersions
  calculated from velocity field are comparable to those calculated
  from the pressure field 
    \MM{The turbulent pressure field has not been
    mentioned in section 3, so you'll need to add a sentence there
    mentioning its presence and behavior to mention it here}, 
    \DL{AP: also mention turbulent pressure found for the bulk of dense gas in the simulation in the phase-space analysis presented in \citet{Pallottini17a} here?}
indicating that contribution from shear is unlikely to dominate the velocity dispersions of the smaller MCCs identified, especially 
at the highest $n_{\rm ncut}$.\label{ftn:veldisp}}. 
On average, the Mach number of the MCCs identified at the highest density threshold is $\mathcal{M} = \sigma_{\rm NT}/c_s\simeq 50$, 
but this depends on the evolutionary stage of \flower.  % see e.g., test_brute/leaf_fields_ss16-28/18.96_10_fields/Mach_cloud-mass.png
This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
We also compute the Mach number from turbulent and thermal pressures following
\begin{equation}
\mathcal{M} \equiv \sqrt{\frac{P_{\rm NT} + P}{ P }}.
\label{eqn:MPress}
\end{equation}
% to track its variation over the evolutionary stages of \flower.

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
(middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
MCCs (star symbols) identified in the two most extreme evolutionary
stages of \flower\ --- accreting phase (left) and starburst phase
(right). Star symbols are color-coded by the density thresholds
$n_{\rm cut}$, as illustrated by the colorbar.
Blue circular symbols shown in the $\alpha_{\rm vir}$-mass plot shows the total virial parameters, including
the stellar contribution (see Equation~\ref{eqn:alpha_tot}).
Literature data in the linewidth-size plots are from \citet{Heyer04a, Rosolowsky05a, Bolatto08a, 
% black dot = extragalactic GMCs in quiescent environments
Leroy15a}, and \citet{Swinbank11a}, and the empirical scaling relations are 
from \citet{Larson81a, Heyer04a, Bolatto08a}.
Data points in the $\alpha_{\rm vir}$-mass figure are taken from
\citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein
(see Fig 4 of \citealt{Kauffmann17b}).   
The gray dotted lines shown in the bottom panels correspond to the various external pressures for 
gas in equilibrium, see Equation~\ref{eqn:v0}.
\label{fig:larsons_single}}
\end{figure*}

@@

% middle
While the virial parameter is typically defined as Equation~\ref{eqn:alpha} in observational studies, as they probes structures that are 
mainly composed of molecular gas only, we also calculate the total virial parameter ($\alpha_{\rm vir, tot}$; Equation~\ref{eqn:alpha_tot}) 
for MCCs of \flower, given the high stellar-to-gas mass ratios of some of them (see \Fig{stellarRatio16}). 
MCCs with the highest stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of 
\Fig{MCC} and \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower. 
This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in
the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influence the overall stability of such MCCs.

@@

>>>>

% ------------------
\section{Numerical Simulations}\label{sec:sim}
The simulations used in this work are described by \citealt{Pallottini17a, Pallottini17b} and are only briefly summarized here.
%
\ncode{Serra}\footnote{Greenhouse in Italian.} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) techniques to achieve high spatial resolution in regions of interest (e.g., regions of high density).
%
In particular, it uses a modified version of \ncode{ramses}
\citep{Teyssier02a} as the AMR backend. The simulation used here
covers a comoving box of 20\,Mpc $h$\pmOne in size. The simulation
zooms in on a target halo of mass $M_{\rm DM}\simeq10^{11} \Msun$. The Lagrangian
region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter
%mm (equivalent baryonic) 
mass resolution of $\simeq 6\times 10^4 \Msun$, 
%mm ($1.2 \times 10^4 \Msun$) [expanded out the meaning, but check if
%I have it right]  Such
     equivalent at initial density to a baryonic mass resolution of $1.2
     \times 10^4 \Msun$.  This 
region is spatially refined with a quasi-Lagrangian criterion based on
a mass threshold, so that a cell is refined if its total dark matter
plus baryonic mass exceeds the mass resolution by a factor of
eight. The final finest refined cell in the zoom in region has size
$l_{\rm cell}\simeq$\,30\,pc (at $z = 6$). 
%mm
%    \MM{Is this really the resolution of dark matter particles?  The baryonic mass (i.e.\ gas) resolution depends on the 
%    local density, which would have to be specified here.} \AP{the setting description has been extended}
     Cell sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
%mm 
%     \MM{Nota Bene!} \AP{This note is discussed in details in the following section. In the simulation we do not treat 5--10 cells as MCs, so I would remove the point from the present} although the resolved scale of 5--10 cells is rather larger.
The models include a chemical network 
following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and
H$_2^+$ \citep{Grassi14a,Bovino16a}. Of particular importance here is
that abundances are calculated using an on-the-fly non-equilibrium
formation of molecular hydrogen scheme  
%mm following \citet{Pallotini17b} [the order had to be reversed for alphabetization]
    described by \citet{Pallottini17a}.

@@

The local sound speed of all identified molecular complexes is much
smaller than their turbulent velocities\footnote{Velocity dispersions
  calculated from velocity field are comparable to those calculated
  from the pressure field 
    \MM{The turbulent pressure field has not been
    mentioned in section 3, so you'll need to add a sentence there
    mentioning its presence and behavior to mention it here}, 
    \DL{AP: also mention turbulent pressure found for the bulk of dense gas in the simulation in the phase-space analysis presented in \citet{Pallottini17a} here?}
indicating that contribution from shear is unlikely to dominate the velocity dispersions of the smaller MCCs identified, especially 
at the highest $n_{\rm ncut}$.\label{ftn:veldisp}}. 
We compute the Mach number from turbulent and thermal pressures following
\begin{equation}
\mathcal{M} \equiv \sqrt{\frac{P_{\rm NT} + P}{ P }}.
\label{eqn:MPress}
\end{equation}
On average, the Mach number of the MCCs identified at the highest density threshold is $\mathcal{M} \simeq6$,
% allss: 0.32 
% In [13]: print(get_Mach_all_clouds(ss11))
%[10.62623949  3.10713402  7.0525831   3.336829   10.36052827  7.24157821
%  7.12323137  6.75282955  9.94086767  7.47769907  3.39894958  3.27304956
%  6.69290803 11.44844494  7.03862716  3.16574077  5.1015787   5.67749554
%  7.35946615  6.89475134  7.2433421  10.57019778 11.78414139  3.93499799
%  6.86173652  7.39686112  8.37197686  6.71749578  2.65304172  6.49617895
%  5.15095491  5.6606244   2.98923849  3.65475035  7.37703114  4.5669722
%  7.18720926  7.35017082  6.03000248  6.36373235 10.16701766  8.3894084
%  3.09284034  4.37994321  4.46497953  5.264101    8.11686     3.05183157
%  7.10365783  6.09513017  8.72517656  5.59659665  3.95290202  9.22726672
%  4.94960657  6.19757621  4.63335759  3.32670022  3.46706217  5.58358069
%  3.41808098  8.31386962  4.26357159  3.684986    4.01853538  3.62917357
%  6.05586465  9.82127908  6.68366736 11.0791874  13.28965621 10.42021747
%  3.04409362  7.21509021  3.63699627  8.12503492  3.20158298]
% allss: 18.96
%In [15]: print(get_Mach_all_clouds(ss12))
%[15.25049689  6.74580503  6.98246499  5.17070655  6.470997    7.02626558
%  4.42663778  6.34460542  4.90603266  3.66900884  4.03260414  6.9539893
%  8.36247744  4.89164338  4.12695121  6.55187227  6.15391173  3.56580625
%  5.74818066  3.81067175  6.65393948  9.10100946  6.35039889  4.78667156
%  5.05517168  6.93886988  5.4830306 ]
but this depends on the evolutionary stage of \flower.  % see also e.g., test_brute/leaf_fields_ss16-28/18.96_10_fields/Mach_cloud-mass.png
% This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
(middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
MCCs (star symbols) identified in the two most extreme evolutionary
stages of \flower\ --- accreting phase (left) and starburst phase
(right). Star symbols are color-coded by the density thresholds
$n_{\rm cut}$, as illustrated by the colorbar.
Literature data in the linewidth-size plots are from \citet{Heyer04a, Rosolowsky05a, Bolatto08a, 
% black dot = extragalactic GMCs in quiescent environments
Leroy15a}, and \citet{Swinbank11a}, and the empirical scaling relations are 
from \citet{Larson81a, Heyer04a, Bolatto08a}.
Data points in the $\alpha_{\rm vir}$-mass figure are taken from
\citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein
(see Fig 4 of \citealt{Kauffmann17b}).   
The gray dotted lines shown in the bottom panels correspond to the various external pressures for 
gas in equilibrium, see Equation~\ref{eqn:v0}.
\label{fig:larsons_single}}
\end{figure*}

@@

% middle
While the virial parameter is typically defined as Equation~\ref{eqn:alpha} in observational studies, as they probes structures that are 
mainly composed of molecular gas only, we calculate the virial parameter including the influence from the stellar component 
for MCCs of \flower (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of 
some of them (see \Fig{stellarRatio16}). 
MCCs with the highest stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of 
\Fig{MCC} and \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower. 
This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in
the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influence the overall stability of such MCCs.

@@

\subsection{Importance of Bulk Motions in Measured Velocity Dispersion}

\begin{figure}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-sigma-kms-bulk_sigma-kms-NT} \\
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
\caption{Velocity dispersions from bulk motions and turbulent motions of \flower in accreting phase (top) and 
quiescent phase (bottom). The accreting phase (\Fig{MCC}) displays a more disturbed morphology compared to the 
quiescent phase, which displays a disk-like morphology (\Fig{MCC28}). 
Most MCCs in the accreting phase have velocity dispersions from turbulent motions higher than those from bulk motions. 
The opposite trend is true in the quiescent phase.
\label{fig:vv}}
\end{figure}

We compare the velocity dispersion from bulk motions versus turbulent motions in \Fig{vv}, for the accreting phase
and the quiescent phase. The accreting phase has a disturbed morphology while the quiescent phase 
displays a disk-like morphology (see \Fig{MCC} and \Fig{MCC28}). 
Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions. The opposite is true for the 
quiescent phase. Second, the two velocity dispersions are of the same order of magnitude. 
This indicates that the .... have an important contribution from large-scale rotation.
\DL{ rewrite: This also poses challenge to measurements and interpretation of .... from existing observations of 
molecular ``clouds'' observed with 
ALMA and VLA. 
n, and so comparison of their dynamics with local clouds via e.g., Larsons relations is not straightforward, and thus, the interpretation of such. 
Meaning a lot of the sigma people infer at the sub-pc scale have a non-negligible contribution from rotation (cf. solely random motion), so it's not immediately fair for observations to say that higher redshift molecular gas are more turbulent based on solely measured velocity dispersion. 
}
